Paper_analyses

### 2021-08-03 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

tmp.df4_full_stim_downs_jun2021_60bins%>%
  subset(!is.na(ground_valence))%>%
  group_by(ssid,ground_valence)%>%
  mutate(mean_abs_arousal = mean(abs(arousal), na.rm = TRUE))%>%
  summarise_at(mean_abs_arousal)

@@

>>>>

tmp.df4_full_stim_downs_jun2021_60bins%>%
  subset(!is.na(ground_valence))%>%
  # group_by(ground_valence)%>%
  ungroup()%>%
  mutate(abs_arousal = abs(arousal), na.rm = TRUE)%>%
  mutate(abs_arousal_z = abs_arousal - mean(abs_arousal, na.rm = TRUE))%>%
  # summarise_at(c('mean_abs_arousal'), median, na.rm = TRUE)
  group_by(ssid,ground_valence_2)%>%
  summarise_if(is.numeric, median, na.rm = TRUE)%>%
  ggplot(aes(ground_valence_2, abs_arousal_z, color = ground_valence_2))+
  geom_point()+
  stat_summary(funy = median, geom = 'pointrange')+
  geom_boxplot()

@@

# does absolute arousal correlate with other variables of interest
tmp.df4_full_stim_downs_jun2021_60bins$abs_arousal<- abs(tmp.df4_full_stim_downs_jun2021_60bins$arousal)

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(ssid_num< 500)%>%
  subset(!is.na(groun_valence))%>%
  group_by(ssid, stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, arousal))+
  geom_point()+
  stat_smooth(aes(group = ssid),method = 'lm', se = F)
    ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(groun_valence))%>%
  group_by(ssid, stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(pup_basCor, abs_arousal))+
  geom_point()+
  geom_smooth(aes(group = ssid),method = 'lm', se = F)+
  ggpubr::stat_cor()+
  facet_grid()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(groun_valence))%>%
  group_by(ssid, stimIAPS,ground_valence_lab)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  group_by(ssid,ground_valence_lab)%>%
  mutate(corar = cor(abs_arousal, pup_basCor, use = "complete"))%>%
  ggplot(aes(ground_valence_lab, corar))+
  # geom_point()
  stat_summary(geom = 'pointrange')

tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, ArousalMeanThisSample))+
  geom_point()+
  ggpubr::stat_cor()

tmp.df4_full_stim_downs_jun2021_60bins %>%
  group_by(stimIAPS)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(ArousalMean, abs_arousal))+
  geom_point()+
  ggpubr::stat_cor()
# this again suggests that there is not too much of a problem in our response format as the absolute would be the equivalent of an scale that encodes for calence (direction)
```
